Make any stupid plot you want

### 2021-04-30 draft/sections/scraps.tex
code section
closing out fig redos + labeling + consistently precip

>>>>

S
This API choice can lead to visualizations that break \textit{continuity} when fed into visualizations with different assumptions about structure. The lack of consistent data model can also mean no consistent way of updating the data and therefore no way of guaranteeing that the views are in sync, in visualizations that consistent of multiple views of the same datasource, such as dashboards\cite{a.sarikayaWhatWeTalk2019,fewDashboardConfusionRevisited2007}.
